Response to reviewers

### 2022-02-16 paper/paper-jsdse/paper-jsdse.tex
Added the response and mark 'Need Help'.

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this, is the wages data made public by Singer and Willett (2003) which can be used to teach generalized linear models, in addition to hierarchical, mixed effects and multilevel. The data records hourly wages of a sample of high school dropouts, from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) (Bureau of Labor Statistics, U.S. Department of Labor 2021a).

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals however that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. The wages data was used to illustrate exploratory longitudinal data analysis in Ilk (2004), and was further developed into a case study for use in the teaching of exploratory data analysis at CENSORED.

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals however that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages.

@@

The next step is tidying to obtain \texttt{hgc} and \texttt{ged}. As the highest grade completed is already exist in \texttt{new\_data\_qnames} and stored in year unit (e.g., 10, 11, 12, 13, and so on), we only rename the column name to be \texttt{hgc\_i} and recode it so we have the factor data type (e.g., 10th grade, 11th grade, and so on). For \texttt{ged}, we only separate the year of survey and the GED status of the individual. Later on, this variable is useful to determine the refreshed high school dropouts data.

@@

\caption{Summary plots to check the cleaned data reveal more cleaning is necessary: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual (id=39) with an unusual wage relative to their years of data (C). Some values of hourly wages are unbelievable, and some individuals have extemely unusual wages in some years.}\label{fig:feature-plot}
\end{figure}

@@

\caption{Re-make of the summary plots of the fully processed data suggest that it is now in a reasonable state: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual with an unusual wage relative to their years of data (C). }\label{fig:fixed-feature-plot}
\end{figure}

>>>>

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this, is the wages data made public by Singer and Willett (2003) in their book, Applied longitudinal data analysis: Modeling change and event occurrence, which can be used to teach generalized linear models, in addition to hierarchical, mixed effects and multilevel models. The data records hourly wages of a sample of high school dropouts, from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) (Bureau of Labor Statistics, U.S. Department of Labor 2021a).

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals, however, that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. The wages data was used to illustrate exploratory longitudinal data analysis in Ilk (2004), and was further developed into a case study for use in the teaching of exploratory data analysis at CENSORED.

@@

The next step is tidying to obtain \texttt{hgc} and \texttt{ged}. Besides that \texttt{hgc} is available in the original data, along with \texttt{ged}, it is used to subset the data to the high school dropouts as in the original data. As the highest grade completed is already exist in \texttt{new\_data\_qnames} and stored in year unit (e.g., 10, 11, 12, 13, and so on), we only rename the column name to be \texttt{hgc\_i} and recode it so we have the factor data type (e.g., 10th grade, 11th grade, and so on). For \texttt{ged}, we only separate the year of survey and the GED status of the individual.

@@

\caption{(A) Summary plots to check the cleaned data reveal more cleaning is necessary: longitudinal profiles of wages for all individuals 1979-2018, (B) boxplots of minimum, median, and maximum wages of each individual, (C) and one individual (id=39) with an unusual wage relative to their years of data. Some values of hourly wages are unbelievable, and some individuals have extemely unusual wages in some years.}\label{fig:feature-plot}
\end{figure}

@@

\caption{Re-make of the summary plots of the fully processed data suggest that it is now in a reasonable state: (A) longitudinal profiles of wages for all individuals 1979-2018, (B) boxplots of minimum, median, (C) and maximum wages of each individual, and one individual with an unusual wage relative to their years of data. }\label{fig:fixed-feature-plot}
\end{figure}

### 2022-02-16 paper/paper.Rmd
Added the response and mark 'Need Help'.

We randomly take 20 samples from the data and plot them, as shown in Figure \ref{fig:sample-plot}.<!--AE comment: "It" implies... Please specify what "it" refers to. This could be done by adding onto the first sentence... "as shown in Figure 2, which shows that some respondents have high variability in wages, particularly 5, 7, and 11." However, 7 and 11 don't seem to have particularly high variability, especially when compared to 18. This whole paragraph needs to be fixed/updated.--> It shows that these respondents have a lot of variability in wages, for example, the IDs in panel numbers 5, 7, and 11. The plot also implies that the samples have a different pattern of mean hourly wages. Some have had flat wages for years but had a sudden increase in one particular year, then it gone down again, while the others experienced an upsurge in their wage, for instance, <!--AE comment: Not panel 9 --> the IDs in panel 9. 
<!--I think there is a narrative step missing here, which is that looking at those samples led you to look at plots that show values for the wage variable over all participants and all years. The phrase “the summary plots” was not enough description for me to know what to expect when I flipped to Figure 3. Please be explicit about what the three plots were, why they were made, and what you were looking for. I think there is another narrative step missing about Figure 3C, which is that after you saw there were outliers you tried to identify which respondents had the extreme values. Again, please spell this out in the text. When you return to the plots for the entire dataset in Figure 5, please make parallel comments. -->However, when checking the summary plots (Figure \ref{fig:feature-plot}), we found that some observations had exceptionally high wages. Some of them, for example respondents in Figure \ref {fig:feature-plot} C had experienced unusual wages only in certain year.

@@

```{r feature-plot, fig.cap = "Summary plots to check the cleaned data reveal more cleaning is necessary: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual (id=39) with an unusual wage relative to their years of data (C). Some values of hourly wages are unbelievable, and some individuals have extemely unusual wages in some years.", fig.width=10, fig.height=4, out.width="100%", cache = FALSE}
```

@@

<!--The next paragraph, which begins “The anomalies are also found” should perhaps be “Similar anomalies were found.” Was it the same respondents with the extremely high wages that showed extremely high number of hours of work? I suspect not, but please be explicit.-->
The anomalies are also found in the total hours of work, where some observations reported as having worked for 420 hours a week in total. According to @MichaelRPergamit2001DWTN, one of the flaws of the NLSY79 employment data is that the NLSY79 collects the information of the working hours since the last interview. Thus, it might be challenging for the respondents to track the within-job hours' changes between survey years, especially for the respondents with fluctuating working hours or seasonal jobs. It even has been more challenging since 1994, after which respondents were only surveyed every other year and thus had to recall two full years’ job history. This shortcoming might also contribute to the fluctuation of one's wages data.

@@

Figure \ref{fig:compare-plot} shows the mean hourly wage before and after the extreme values are replaced. It implies that the fluctuation can still be observed in the data after the treatment. However, the large spikes, which are considered "erroneous outliers", are already eliminated from the data. Hence, the model produces a data set with a more reasonable degree of fluctuation.

@@

```{r fixed-feature-plot, fig.cap = "Re-make of the summary plots of the fully processed data suggest that it is now in a reasonable state: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual with an unusual wage relative to their years of data (C). ", fig.width=10, fig.height=4, out.width="100%", cache = FALSE}
```

@@

- determining which records should be downloaded from the database.
- calculating experience in the workforce requires comparing the date of first job with the first year the individual was recorded, both of which are available in the database. 
- there are many unusually high hourly wages, e.g. greater than $30,000 per hour.
- there is no explicit variable in the database recording high school dropout, which means we needed to compare the date of 12th grade with the individual's age.
- matching id's from the original data with those in the refreshed data, do refer to the same person based on the demographic information available.

>>>>

We randomly take 20 samples from the data and plot them, as shown in Figure \ref{fig:sample-plot}.<!--AE comment: "It" implies... Please specify what "it" refers to. This could be done by adding onto the first sentence... "as shown in Figure 2, which shows that some respondents have high variability in wages, particularly 5, 7, and 11." However, 7 and 11 don't seem to have particularly high variability, especially when compared to 18. This whole paragraph needs to be fixed/updated.--> It shows that these respondents have a lot of variability in wages, for example, the IDs in panel numbers 5, 7, and 11. The plot also implies that the samples have a different pattern of mean hourly wages. Some have had flat wages for years but had a sudden increase in one particular year, then it gone down again, while the others experienced an upsurge in their wage, for instance, <!--AE comment: Not panel 9 --> the IDs in panel 9. 
<!--I think there is a narrative step missing here, which is that looking at those samples led you to look at plots that show values for the wage variable over all participants and all years. The phrase “the summary plots” was not enough description for me to know what to expect when I flipped to Figure 3. Please be explicit about what the three plots were, why they were made, and what you were looking for. I think there is another narrative step missing about Figure 3C, which is that after you saw there were outliers you tried to identify which respondents had the extreme values. Again, please spell this out in the text. When you return to the plots for the entire dataset in Figure 5, please make parallel comments. -->
However, when checking the summary plots (Figure \ref{fig:feature-plot}), we found that some observations had exceptionally high wages, the maximum value of the wages unbelievably reached about $60,000/hour. Besides, some of them, for example respondents in Figure \ref {fig:feature-plot} C, had experienced unusual wages only in certain year.

@@

```{r feature-plot, fig.cap = "Summary plots to check the data after the tidying stage: (A) longitudinal profiles of wages for all individuals 1979-2018, (B) boxplots of minimum, median, and maximum wages of each individual, (C) and one individual (id=39) with an unusual wage relative to their years of data. It reveals that some values of hourly wages are unbelievable, and some individuals have extemely unusual wages in some years. Accordingly, more cleaning is necessary to treat these extreme values.", fig.width=10, fig.height=4, out.width="100%", cache = FALSE}
```

@@

<!--The next paragraph, which begins “The anomalies are also found” should perhaps be “Similar anomalies were found.” Was it the same respondents with the extremely high wages that showed extremely high number of hours of work? I suspect not, but please be explicit.-->
Extremely high values were also found in the total hours of work, where some observations reported as having worked for 420 hours a week in total. According to @MichaelRPergamit2001DWTN, one of the flaws of the NLSY79 employment data is that the NLSY79 collects the information of the working hours since the last interview. Thus, it might be challenging for the respondents to track the within-job hours' changes between survey years, especially for the respondents with fluctuating working hours or seasonal jobs. It even has been more challenging since 1994, after which respondents were only surveyed every other year and thus had to recall two full years’ job history. This shortcoming might also contribute to the fluctuation of one's wages data.

@@

Figure \ref{fig:compare-plot} shows the mean hourly wage before and after the extreme values are replaced. The figure shows that fluctuations in wages still exist even in the imputed data. However, the large spikes, which are considered "erroneous outliers", are already eliminated from the data. Hence, the model produces a data set with a more reasonable degree of fluctuation.

@@

```{r fixed-feature-plot, fig.cap = "Re-make of the summary plots of the fully processed data suggest that it is now in a reasonable state: (A) longitudinal profiles of wages for all individuals 1979-2018, (B) boxplots of minimum, median, (C) and maximum wages of each individual, and one individual with an unusual wage relative to their years of data. ", fig.width=10, fig.height=4, out.width="100%", cache = FALSE}
```

@@

- determining which records should be downloaded from the database.
- calculating experience in the workforce requires comparing the date of first job with the first year the individual was recorded, both of which are available in the database. 
- treating the extreme values since there are many unusually high hourly wages, e.g. greater than $60,000 per hour.
- determining the dropouts subset as there is no explicit variable in the database recording high school dropout, which means we needed to compare the date of 12th grade with their GED status.
- matching ID's from the original data with those in the refreshed data, do refer to the same person based on the demographic information available.

### 2022-02-16 paper/paper.tex
Added the response and mark 'Need Help'.

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this, is the wages data made public by Singer and Willett (2003) which can be used to teach generalized linear models, in addition to hierarchical, mixed effects and multilevel models. The data records hourly wages of a sample of high school dropouts, from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) (Bureau of Labor Statistics, U.S. Department of Labor 2021a).

>>>>

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this, is the wages data made public by Singer and Willett (2003) in their book, Applied longitudinal data analysis: Modeling change and event occurrence, which can be used to teach generalized linear models, in addition to hierarchical, mixed effects and multilevel models. The data records hourly wages of a sample of high school dropouts, from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) (Bureau of Labor Statistics, U.S. Department of Labor 2021a).

### 2022-02-16 response/response1.Rmd
Added the response and mark 'Need Help'.

@@

@@

@@

@@

@@

* We have filter the x-axis of the refreshed data set until 1994, so they are comparable.

@@

* Fluctuation is the variability in the data (up and down in the wages), while treatment is imputing the extremely high wages (anomaly) with their RLM's predicted value. The detail explanation of fluctation is discussed in Subsection 3.3 Initial Data Analysis, while the treatment is explained in Subsection 3.4 (Paragraph 3).

>>>>

* We have made this sentences more explicit that the extremely high values were also observed in the `total hours of work`.

@@

* We have replaced this sentences as per the suggestion.

@@

* We have added the specifity of the extremely high wages in Subsection 3.3. Initial Data Analysis. We have also edited every bullet so it started with verb -ing.

@@

* We have edited the caption.

@@

* We have moved the letter label before the description.

@@

* We have filtered the x-axis of the refreshed data set until 1994, so they are comparable.

@@

* Fluctuation is the variability in the data (up and down) in the wages, while treatment is imputing the extremely high wages (anomaly) with their RLM's predicted value. The detail explanation of fluctation is discussed in Subsection 3.3 Initial Data Analysis, while the treatment is explained in Subsection 3.4 (Paragraph 3). We also have edited this sentences to avoid implicity.
